The Two Dualities of Computation: Negative and Fractional Types

### 2012-03-08 rational.tex
logical rev. prop.

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Graphical Language}

@@

%%%%%%%%%%%%%%%%%%%
\subsection{Semantics}

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Graphical Language}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Semantics}

@@

\roshan{We really have to rethink this prop in the precense of
  negatives and fractionals. With negatives, the program can actually
  end at the begining of the circuit -- i.e. the program {{c:b1<->b2}}
  can stop with a value of type {{b1}}. With fractionals, there can be
  several values of type {{b2}} produced for a value of type {{b1}}. }
